---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(vacancesscolr)
```

# vacancesscolr

The goal of `vacancesscolr` is to be able to quickly retrieve school holidays in France for the 2008-2018 period.

The data used in this package has been obtained from [Antoine Augusti's vacances-scolaires dataset](https://github.com/AntoineAugusti/vacances-scolaires), under the Etalab license (open license).

## Installation

`vacancesscolr` lives only on Github for now. Please use `devtools` or `remotes` to install it.

``` r
# devtools::install_github("tutuchan/vacancesscolr")
# remotes::install_github("tutuchan/vacancesscolr")
```

## Examples

Check if a date is a holiday:

```{r check}
is_holiday("2018-03-05")
is_holiday("2018-03-05", zone = "A")
is_holiday("2018-03-05", zone = "B")
```

Retrieve all holidays for a year, optional zone and optional type of holiday:

```{r year}
get_year_holidays(2018, name = "Vacances d'hiver")
```

You can use shortened names for the holidays names:

```{r names}
full_holidays_names()

short_holidays_names()
```

