---
output: 
  github_document:
    df_print: "tibble"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(vacancesscolr)
```

# vacancesscolr

The goal of `vacancesscolr` is to be able to quickly retrieve school holidays in France for the 2008-2018 period and bank holidays for any given year.

The data used in this package has been obtained from [Antoine Augusti's vacances-scolaires dataset](https://github.com/AntoineAugusti/vacances-scolaires), under MIT license. 

The functionalities are direct ports from his [vacances-scolaires-france](https://github.com/AntoineAugusti/vacances-scolaires-france) and [jours-feries-france](https://github.com/AntoineAugusti/jours-feries-france) Python packages.

## Installation

`vacancesscolr` lives only on Github for now. Please use `devtools` or `remotes` to install it.

``` r
# devtools::install_github("tutuchan/vacancesscolr")
# remotes::install_github("tutuchan/vacancesscolr")
```

## Examples

**Please note that data.frames are printed as `tibble`s in this README for clarity but they are simple `data.frame`s in R.**

### Holidays

Check if a date is a holiday:

```{r check}
is_holiday("2018-03-05")
is_holiday("2018-03-05", zone = "A")
is_holiday("2018-03-05", zone = "B")
```

Retrieve all holidays for a year, optional zone and optional type of holiday:

```{r year}
get_year_holidays(2018, name = "Vacances d'hiver")
```

You can use shortened names for the holidays names:

```{r names}
holidays_names_full()

holidays_names_short()
```

### Bank holidays

Get all bank holidays for a year:

```{r bank holidays}
get_year_bank_holidays(2018)
```

Get a specific bank holiday:

```{r specific bank holiday}
bh_lundi_paques(2018)
```

Get the names of bank holidays (some have multiple ways to call them):

```{r bank holidays names}
bank_holiday_names()

bank_holiday_names_unique()
```

Get a bank holiday knowing its name:

```{r bank holiday}
bank_holiday("1 mai")(2018)
```

